\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5} % Added for the link icon

% Section Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% List Formatting
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Donil Jaison}} \\
    \vspace{3pt}
    \href{mailto:donil.j23@iiits.in}{donil.j23@iiits.in} $|$ \href{https://github.com/doniljaison}{github.com/doniljaison} $|$ \href{https://linkedin.com/in/donil-jaison-93a17428a}{linkedin.com/in/donil-jaison} \\
    Thrissur, Kerala $|$ +91 9747109684
\end{center}

\vspace{-5pt}

% Education
\section*{EDUCATION}
\noindent\textbf{Indian Institute of Information Technology, Sri City} \hfill Expected May 2027 \\
Bachelor of Technology in Computer Science and Engineering \hfill \textbf{CGPA: 7.7/10.0} \\
\vspace{6pt}

\noindent\textbf{The Indian School, Kingdom of Bahrain} \\
Class XII (CBSE): Computer Science, Mathematics, Physics \hfill 2023 $|$ \textbf{94.6\%} \\
Class X (CBSE) \hfill 2021 $|$ \textbf{91.6\%}

% Skills
\section*{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Languages:} Python, Java, JavaScript (ES6+), SQL, HTML5, CSS3, C.
    \item \textbf{Course Work:} DBMS, Object-Oriented Programming, DSA, Operating Systems, Computer Networks.
    \item \textbf{Frameworks:} Node.js, Express.js, React.js, Pandas, NumPy, Matplotlib.
    \item \textbf{Tools \& Core:} Git, GitHub, MongoDB, AWS, REST, SOAP, GraphQL, Linux.
\end{itemize}

% PROJECTS
\section*{PROJECTS}

\noindent\
{\textbf{Sports Event Management System}} \href{https://github.com/SportsAmigo/SportsAmigo}{\small\faExternalLink*} \hfill Dec 2025 \\
\textit{A role-based event platform; owned the Manager Module and co-designed system architecture}
\begin{itemize}
    \item Engineered the complete \textbf{Manager Dashboard} using React.js and Node.js, enabling users to manage team rosters, register for events, and track match schedules.
    \item Collaborated with a team of 3 to design the \textbf{database schema} and API structure, establishing the core logic for Role-Based Access Control (RBAC).
    \item Implemented real-time state management and optimized data fetching to ensure seamless synchronization between the dashboard and backend services.
\end{itemize}

\vspace{4pt}
\noindent\
{\textbf{GRASP Algorithm Optimization}} \href{https://github.com/doniljaison/ai-project}{\small\faExternalLink*} \hfill Nov 2024 \\
\textit{A research initiative optimizing sparse graph algorithms using machine learning}
\begin{itemize}
    \item Implemented a greedy randomized adaptive search procedure (GRASP) for sparse graph optimization, focusing on \textbf{complexity analysis} and heuristic efficiency.
    \item Integrated machine learning enhancements to guide the search process, improving solution quality by \textbf{15\%} over standard baseline algorithms.
    \item Conducted extensive performance testing and algorithmic analysis, documenting time-complexity trade-offs in a technical report.
\end{itemize}

\vspace{4pt}
\noindent\
{\textbf{EcoRoute - Logistics Optimization Engine}} \href{https://doniljaison.github.io/ecoroute-optimizer/}{\small\faExternalLink*} \hfill Sept 2025 \\
\textit{A data analytics engine optimizing logistics for sustainability and cost efficiency}
\begin{itemize}
    \item Engineered a data processing pipeline using \textbf{Python and Pandas} to analyze over 9,000+ shipping records, identifying routing inefficiencies.
    \item Built an interactive algorithm-driven model to score carrier strategies based on cost vs. sustainability metrics.
    \item Developed a frontend visualization dashboard to render complex datasets into actionable insights, helping optimize routing paths for reduced carbon footprint.
\end{itemize}

\vspace{4pt}
\noindent\
{\textbf{Global Sales Data Analytics}} \href{https://doniljaison.github.io/product-sales-analytics/}{\small\faExternalLink*} \hfill Dec 2025 \\
\textit{A data visualization tool for detecting regional performance anomalies}
\begin{itemize}
    \item Processed and cleaned a dataset of \textbf{51,290+ transactions} using Python, performing statistical analysis to detect regional sales trends.
    \item Created dynamic heatmaps and temporal trend visualizations to represent large-scale sales data programmatically.
\end{itemize}

% Achievements
\section*{ACHIEVEMENTS \& LEADERSHIP}
\begin{itemize}
    \item \textbf{Assistant House Captain:} Led a student body of 100+, organizing large-scale logistics for school-wide events and fostering team collaboration.
    \item \textbf{Principal's List:} Awarded for academic excellence in CBSE Class 12th Results.
    \item \textbf{Competitive Sports:} Represented school in Badminton (CBSE Cluster tournaments) and secured medals in National-level Karate competitions.
\end{itemize}

\end{document}